What public transit API logs tell us about travel flows

### 2016-01-14 paper.tex
Citation added

%Visualizations are crucial for understanding the patterns in data and representing transit flows.
Visualizations are crucial for making data analysis tangible, so that results can be communicated and debated \cite{robinson2008collaborative}. 
This is key for our research, since the questions presented are exploratory in nature \cite{kraak2008exploratory} and can be addressed in many ways. 
Movement data has received substantial attention from the visualization community and a range of techniques has been developed to support flow analysis \cite{andrienko2012visual}. 
Visualizations of flows can be broadly categorized into two groups. 
Representations that display the complete trajectory and Origin Destination (OD) type representations that take only the start and end locations into account.
Since our data solely consists of OD information, we narrow our description to the latter group of visualization techniques.

OD type representations are employed when the origin and destination preside over intermediate locations on the path of movement. The OD Matrix is the most common visualization technique based on this type of representation. 
Rows and columns correspond to locations while cells are coloured to express the volume of flow.
OD matrices can be reordered to emphasise connectivity between locations.
While this feature is particularly useful for identifying trends and outliers in the data, the tabular display is challenging for lay users to interpret and less expressive of connections between locations than representations based on the node-link metaphor.
In recent years, such representations have become increasingly prominent for displaying movement in science as well as popular culture.
Locations are depicted as nodes and arrows are drawn between them to indicate movement in a certain direction, allowing for exact and individual relationships to be traced. 
This representation is detailed and straightforward to understand but becomes cluttered when multiple lines intersect.

>>>>

%Visualizations are crucial for understanding the patterns in data and representing transit flows.
Visualizations are crucial for making data analysis tangible \cite{thomas2006visual}, so that results can be communicated and debated \cite{robinson2008collaborative}. 
This is key for our research, since the questions presented are exploratory in nature \cite{kraak2008exploratory} and can be addressed in many ways. 
Movement data has received substantial attention from the visualization community and a range of techniques has been developed to support flow analysis \cite{andrienko2012visual}. 
Visualizations of flows can be broadly categorized into two groups. 
Representations that display the complete trajectory and Origin Destination (OD) type representations that take only the start and end locations into account.
Since our data solely consists of OD information, we narrow our description to the latter group of visualization techniques.

OD type representations are employed when the origin and destination preside over intermediate locations on the path of movement. The OD Matrix is the most common visualization technique based on this type of representation. 
Rows and columns correspond to locations while cells are coloured to express the volume of flow.
OD matrices can be reordered to emphasise connectivity between locations.
While this feature is particularly useful for identifying trends and outliers in the data, the tabular display is challenging for lay users to interpret and less expressive of connections between locations than representations based on the node-link metaphor \cite{holten2011extended}.
In recent years, such representations have become increasingly prominent for displaying movement in science as well as popular culture.
Locations are depicted as nodes and arrows are drawn between them to indicate movement in a certain direction, allowing for exact and individual relationships to be traced. 
This representation is detailed and straightforward to understand but becomes cluttered when multiple lines intersect.
